---
title: "Codealong_6"
author: "Jake Nyiri"
date: "11/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(palmerpenguins)
library(ggpubr)
library(broom)
```
```{r}
#Create sample vectors, set seed so random generation matches ones from lab
set.seed(1414)
gp_1<- sample.int(20, size = 15,replace = TRUE)
set.seed(1424)
gp_2<- sample.int(30, size = 15, replace = TRUE)

```

```{r}
#baser hist function which I wish Id known existed
hist(gp_1)
hist(gp_2)

```

```{r}
#Run tw0-sample unpaired rank test (WM test )
my_wmu <- wilcox.test(gp_1,gp_2)
#error is normal because some values repeated in vectors
```
```{r}
#Duh plot of penguins
penguin_plot<-penguins %>% 
  ggplot(aes(x=flipper_length_mm, y=body_mass_g))+
  geom_point()

penguin_plot
```
```{r}
#duh linear model of penguins
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data=penguins)
#summary gets summary info for linear model
summary(penguin_lm)
```
```{r}
#clean it up and present it
penguin_lm_tidy <- broom::tidy(penguin_lm)
penguin_lm_tidy
#intercept is (intercept), slope is flipper_length_mm
```
```{r}
#this pulls out individual values for the intercept and slope from the summary
penguin_int <- penguin_lm_tidy$estimate[1]
penguin_int

penguin_coef <- penguin_lm_tidy$estimate[2]
penguin_coef
```
```{r}
#Kind of tedious, can get some metrics easier
penguin_lm_out <- broom::glance(penguin_lm)
penguin_lm_out
```
This code frustratingly utilizes actual model values and can be re-used but has no explanation! So no idea what it's doing.

"Simple linear regression was used to explore the relationship between penguin flipper length (mm) and body mass (g) across all three penguin species, and including both male and female penguins. A significant regression model was found ($\beta$ = `r round(penguin_coef,3)`, F(`r penguin_lm_out$df`,`r penguin_lm_out$df.residual`) = `r round(penguin_lm_out$statistic,1)`, p < 0.001) with an R^2^ of `r round(penguin_lm_out$r.squared,3)`."

```{r}
#This somehow magically creates the four graphsd to check the residuals for stuff
plot(penguin_lm)

```

```{r}
#make a graph with the eqn superimposed
ggplot(data=penguins, aes(x=flipper_length_mm, y=body_mass_g))+
  geom_point()+
  geom_smooth(method="lm", #creates new lm, doesn't add penguin_lm?
              color="red",
              size = 0.5,
              fill = "gray10",
              alpha = 0.5) + #trans[arency of the eqn added
  theme_light()+
  #this adds the eqn for the generated lm to the graph, x and y are where it is added
  ggpubr::stat_regline_equation(label.x = 180, label.y = 5700)
```
```{r}
penguins_cor <- cor.test(penguins$flipper_length_mm, penguins$body_mass_g)
penguins_cor
#This show pearson's R of 0.87, strong positive correlation  between flipper lwngth and body mass
```

